Phylogenetics

### 2025-04-07 episodes/phylogenetics.Rmd
Done updating phylogenetics

On other computer, just open the file with the regular File > Open menu.

@@

Get to the right folder, require compute time and load the right modules.

@@

@@

Here, we tell IQ-TREE to use the alignment `rpoB.einsi.clipkit.aln`, and to test among the standard substitution models which one fits best (`-m TEST`). We also tell IQ-TREE to perform 1000 ultra-fast bootstraps (`-B 1000`). We'll discuss these later.

@@

Redo a ML tree from the other alignment (FFT-NS) we inferred with `mafft` and display the resulting tree in FigTree

@@

@@

Import the tree on your computer and load it with FigTree or with [phylo.io](https://beta.phylo.io/viewer/#)

@@

Hint: what are *Glycine* and *Arabidopsis*? What about *Synechocystis* and *Microcystis*?

Hint: search for the accession number of the *Glycine* RpoB sequence on [NCBI](https://www.ncbi.nlm.nih.gov/search/). Any hint there?

@@

In my simulations, no allele got fixed, the final allele frequencies range 
20-80%

>>>>

On other computers, just open the file with the regular File > Open menu.

@@

Get to the right folder, require compute time and load the right modules. The project is `uppmax2025-3-4`. The module containing IQ tree is called `iqtree`.

::: hint

 ```bash
interactive ...
module load ...
```

@@

 ```bash
interactive -A <project> -M <cluster> -t <time>
module load <general bioinfo module> iqtree
```

::: instructor

@@

Here, we tell IQ-TREE to use the alignment `-s rpoB.einsi.clipkit.aln`, and to test among the standard substitution models which one fits best (`-m TEST`). We also tell IQ-TREE to perform 1000 ultra-fast bootstraps (`-B 1000`). We'll discuss these later.

@@

Redo a ML tree from the other alignment (FFT-NS) we inferred with `mafft` and display the resulting tree in FigTree.

::: hint

```bash
iqtree2 -h
```
::::::::

@@

```bash
iqtree2 -s <alignment file> <option and text for testing model> <option and test for 1000 fast bootstraps> 
```

Import the tree **on your computer** and load it with FigTree or with [phylo.io](https://beta.phylo.io/viewer/#)

:::::::::::::::::::::::: instructor

@@

@@

::: hint

What are *Glycine* and *Arabidopsis*? What about *Synechocystis* and *Microcystis*?

::::::::

::: hint

Search for the accession number of the *Glycine* RpoB sequence on [NCBI](https://www.ncbi.nlm.nih.gov/search/). Any hint there?

::::::::

@@

In my simulations, no allele got fixed, the final allele frequencies range20-80%
